### 2019-05-02 2-Chapters/3-Chapter/chapter3.tex
Fixed typos

In this section, we use the SMPyBandits library to compare experimentally various state-of-the-art single-player algorithms on different kinds of multi-armed bandit problems.
First, we detail the list of $9$ different algorithms that we compare, and the different problems on which they are all tested.
We give the results of the numerical experiments, in terms of mean regret at the end of the experiment of different horizons $T$.
Additional results in terms of real measurements of time and memory are given and discussed in the next Section~\ref{sec:3:timeAndMemoryCosts}.

@@

\TODOL{FIXME launch these experiments, for a very short number of repetitions N=4, and if I'm happy about the results and if they are easily copied-and-pasted here, then launch with N=100 or N=1000 depending on the running

% DEBUG=True; NOPLOTS=False; SAVEALL=False; for N in 4 100 1000; do for BAYES in False True; do for T in 1000 5000 10000 50000; do for K in 2 5 10 20 50; do debut=$(date); DEBUG=$DEBUG NOPLOTS=$NOPLOTS SAVEALL=$SAVEALL N=$N N_JOBS=-1 T=$T K=$K BAYES=$BAYES make --noFreeSMS single && cp logs/main_py3_log.txt logs/main_py3_log__N${N}_BAYES${BAYES}_T{T}_K{K}.txt && FreeSMS.py "Expérience commencée ${debut} terminée, avec N=${N}, BAYES=${BAYES}, T=${T}, K=${K}." ; done; done; done; done time.}

@@

\begin{footnotesize}

@@

\end{footnotesize}

@@

@@

\end{itemize}
\TODOL{FIXME order correctly in configuration.py}

@@

Finally, we give below the Bash command that was used to run the experiments presented in Sections~\ref{sec:3:reviewSPAlgorithms} and \ref{sub:3:additionalExperiments}.
It uses \texttt{for} loops from Bash and not Python and environment variables, but we could also have done the same by writing a Python script that calls the \texttt{main.py} script for the different values of $N$, $T$ and $K$.

% https://tex.stackexchange.com/a/12430/
\begin{listing}[h!]
    \begin{minted}[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{bash}
$ for N in 4 100 1000; do \
  for BAYES in False True; do\
  for T in 1000 5000 10000 50000; do \
  for K in 2 5 10 20 50; do \
    DEBUG=False NOPLOTS=False SAVEALL=True N_JOBS=-1 \
             N=$N BAYES=$BAYES T=$T K=$K make single \
    && cp logs/main_py3_log.txt logs/main_py3_log__N${N}_BAYES${BAYES}_T{T}_K{K}.txt \
  done; done; done; done
    \end{minted}
    \caption{Snippet of Bash code to run the large experiments presented in Sections~\ref{sec:3:reviewSPAlgorithms} and \ref{sub:3:additionalExperiments}.
    % \captionof{listing}{Small snippet of Bash code to run an experiment \label{lst:3:BashCodeToLaunchLargeExperiments}.}
    \label{lst:3:BashCodeToLaunchLargeExperiments}
\end{listing}

>>>>

In this section, we use the SMPyBandits library to compare experimentally various state-of-the-art single-player algorithms on different kinds of multi-armed bandit problems.
First, we detail the list of different algorithms that we compare, and the different problems on which they are all tested.
We give the results of the numerical experiments, in terms of mean regret at the end of the experiment of different horizons $T$.
Additional results in terms of real measurements of time and memory are given and discussed in the next Section~\ref{sec:3:timeAndMemoryCosts}.

@@

\TODOL{FIXME launch these experiments, for a very short number of repetitions N=4, and if I'm happy about the results and if they are easily copied-and-pasted here, then launch with N=100 or N=1000 depending on the running time of the whole simulations}

% DEBUG=True; NOPLOTS=False; SAVEALL=False; for N in 4 100 1000; do for BAYES in False True; do for T in 1000 5000 10000 50000; do for K in 2 5 10 20 50; do debut=$(date); DEBUG=$DEBUG NOPLOTS=$NOPLOTS SAVEALL=$SAVEALL N=$N N_JOBS=-1 T=$T K=$K BAYES=$BAYES make --noFreeSMS single && cp logs/main_py3_log.txt logs/main_py3_log__N${N}_BAYES${BAYES}_T{T}_K{K}.txt && FreeSMS.py "Expérience commencée ${debut} terminée, avec N=${N}, BAYES=${BAYES}, T=${T}, K=${K}." ; done; done; done; done time.

@@

\begin{footnotesize}  % WARNING

@@

\end{footnotesize}  % WARNING

@@

In this Appendix, we start by giving a small but complete example of use of SMPyBandits, then we give additional experimental results completing those presented in Section~\ref{sec:3:reviewSPAlgorithms} and \ref{sec:3:timeAndMemoryCosts} above.
We conclude by a discussion on parallel computations and the use of multi-core CPU to speed-up simulations in SMPyBandits.

@@

\end{itemize}

@@

Finally, we give below in Listing~\ref{lst:3:BashCodeToLaunchLargeExperiments} the Bash command that was used to run the experiments presented in Sections~\ref{sec:3:reviewSPAlgorithms} and \ref{sub:3:additionalExperiments}.
It uses \texttt{for} loops from Bash and not Python and environment variables, but we could also have done the same by writing a Python script that calls the \texttt{main.py} script for the different values of $N$, $T$ and $K$.

% https://tex.stackexchange.com/a/12430/
\begin{listing}[h!]
    \begin{minted}[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{bash}
$ for N in 4 100 1000;            do \
  for BAYES in False True;        do \
  for T in 1000 5000 10000 50000; do \
  for K in 2 5 10 20 50;          do \
    DEBUG=False NOPLOTS=False SAVEALL=True N_JOBS=-1 \
                         N=$N BAYES=$BAYES T=$T K=$K \
                    python3 main.py configuration.py \
    && cp logs/main_py3_log.txt \
          logs/main_py3_log__N${N}_BAYES${BAYES}_T{T}_K{K}.txt \
  done; done; done; done
    \end{minted}
    \caption{Snippet of Bash code to run the large experiments presented in Sections~\ref{sec:3:reviewSPAlgorithms} and \ref{sub:3:additionalExperiments}.}
    % \captionof{listing}{Small snippet of Bash code to run an experiment \label{lst:3:BashCodeToLaunchLargeExperiments}.}
    \label{lst:3:BashCodeToLaunchLargeExperiments}
\end{listing}

### 2019-05-02 2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits_appendix.tex
Fixed typos

Putting things together, we showed that
\[\KL\left(\Pr_{\bm{\mu}}^{\cO_t},\Pr_{\bm{\lambda}}^{\cO_t}\right) = \KL\left(\Pr_{\bm{\mu}}^{\cO_{t-1}},\Pr_{\bm{\lambda}}^{\cO_{t-1}}\right) + \E_{\bm{\mu}}  \left[\sum_{k=1}^K \indic{(A^j(t)=k)} \kl \left(\mu_{k},\lambda_{k}\right)\right] + \smallO{\log(T)}.\]
Iterating this equality and using that $\KL\left(\Pr_{\bm{\mu}}^{\cO_{0}},\Pr_{\bm{\lambda}}^{\cO_{0}}\right)=0$ yields that
\[\sum_{k=1}^{K}\E_{\bm{\mu}}\left[T_k^j(T)\right]\kl(\mu}_k,\lambda_k) \geq \kl \left(\Pr_{\bm{\mu}}(A),\Pr_{\bm{\lambda}}(A)\right) + \smallO{\log(T)},\]
for all $A \in \sigma(\cO_T)$, in particular for all $A \in \cF^j_T$.

>>>>

Putting things together, we showed that
\[\KL\left(\Pr_{\bm{\mu}}^{\cO_t},\Pr_{\bm{\lambda}}^{\cO_t}\right) = \KL\left(\Pr_{\bm{\mu}}^{\cO_{t-1}},\Pr_{\bm{\lambda}}^{\cO_{t-1}}\right) + \E_{\bm{\mu}}  \left[\sum_{k=1}^K \indic{(A^j(t)=k)} \kl \left(\mu_{k},\lambda_{k}\right)\right] + \smallO{\log(T)}.\]
Iterating this equality and using that $\KL\left(\Pr_{\bm{\mu}}^{\cO_{0}},\Pr_{\bm{\lambda}}^{\cO_{0}}\right)=0$ yields that
\[\sum_{k=1}^{K}\E_{\bm{\mu}}\left[T_k^j(T)\right]\kl(\mu_k,\lambda_k) \geq \kl \left(\Pr_{\bm{\mu}}(A),\Pr_{\bm{\lambda}}(A)\right) + \smallO{\log(T)},\]
for all $A \in \sigma(\cO_T)$, in particular for all $A \in \cF^j_T$.
